Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-08 sas2015/content/appendix.tex

\section*{Appendix}
In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca}, the table illustrating frequencies of correlated calls from Section~\ref{}, and the code discussed in Section~\ref{sec:collex}.

>>>>

\section{TraversableOnce Trait from Scala Standard Library}

In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca}, the table illustrating frequencies of correlated calls from Section~\ref{}, and the code discussed in Section~\ref{sec:collex}.
\begin{figure}
\inputMinted{scala}{TraversableOnce.scala}
\caption{Relevant code from \textsf{TraversableOnce} and related traits.}
\label{fig:traversableonce}
\end{figure}

\section{Proofs}

### 2015-03-08 sas2015/content/example.tex

\section{Background and Motivation}
  \label{sec:MotivatingExample}

In this section, we illustrate our approach using a small motivating example that
shows how our technique improves the precision of taint analysis.
A taint analysis is a specialized data-flow analysis for computing how string values
may flow from ``sources'', which are typically statements that read untrusted input, 
to ``sinks'', which are typically security-sensitive
operations such as calls to 
a database. In previous research~\cite{DBLP:conf/issta/GuarnieriPTDTB11,DBLP:conf/pldi/ArztRFBBKTOM14}, 
taint analysis algorithms have been formulated as IFDS problems.

@@

Figure~\ref{list:ccexample} shows a small Java program that we will use to illustrate
how our technique improves the precision of a simple taint analysis. The program
declares a class \code{A} with a subclass \code{B},  where \code{A} defines methods 
\code{foo()} and \code{bar()} that are overridden in \code{B}.  
%In order to keep the example small and self-contained, 
It is assumed  that secret values are created by 
an unspecified function \code{secret()}, which is called in method \code{A.foo()}%
%  on line~\ref{line:Afoo}
. Furthermore, it is assumed that any write to the standard output 
stream via calls \code{System.out.println()} such as the one in method \code{B.bar()} 
%on line~\ref{line:Bbar} 
is a security-sensitive operation. Depending on the number of 
arguments passed to the program, the \code{main()} method of the example program creates 
either an \code{A}-object or a \code{B}-object%
%on line~\ref{line:createObject}
. The 
program then calls \code{foo()} on this object
on line~\ref{line:callfoo}, which is 
followed by a call to \code{bar()} on the same object%
%on line~\ref{line:callbar}
.

The specific question that we would like to answer for the example program of
Figure~\ref{list:ccexample} is the following: Is it possible for the untrusted value 
that is read on line~\ref{line:Afoo} to flow to the print statement% %on line~\ref{line:Bbar}
?
To determine whether such a flow of tainted data is possible, consider the control-flow
supergraph for the example program that is shown in Figure~\ref{fig:examplesupergraph}.
 The nodes in this graph correspond to statements, method entry points (start nodes) and 
method exit points (end nodes). Note that for each method call, the graph contains a 
distinct call-node and a return-node. Edges in the graph reflect intraprocedural control flow, 
flow of control from a caller to a callee (edges from call-nodes to start-nodes), or
flow of control from a callee back to a caller (edges from end-nodes to return-nodes).

In the case of our example, the control flow within each of the methods is straightforward and
all interesting issues arise from interprocedural control flow. In particular,
note that, since the variable \code{a} may point to either an \code{A}-object or a \code{B}-object, 
the call on line~\ref{line:callfoo} may dispatch to either \code{A.foo()} or to \code{B.foo()},
and this is reflected by edges  
  from the node labeled $\highlight{\code{call}_\code{foo}}{greyblue}$ to the nodes labeled
  $\highlight{\code{start}_\code{A.foo()}}{bisque}$ and $\highlight{\code{start}_\code{B.foo()}}{lightsalmonpink}$
and by edges
  from the nodes labeled $\highlight{\code{end}_\code{A.foo}}{bisque}$ and $\highlight{\code{end}_\code{B.foo}}{lightsalmonpink}$ 
  to the node labeled  $\highlight{\code{return}_\code{foo}}{greyblue}$.  
Similarly, there are edges from the node labeled $\highlight{\code{call}_\code{bar}}{greyblue}$ to the nodes 
$\highlight{\code{start}_\code{A.bar()}}{bisque}$ and $\highlight{\code{start}_\code{B.bar()}}{lightsalmonpink}$, and 
edges
  from the nodes labeled $\highlight{\code{end}_\code{A.bar}}{bisque}$ and $\highlight{\code{end}_\code{B.bar}}{lightsalmonpink}$ 
  to the node labeled  $\highlight{\code{return}_\code{bar}}{greyblue}$.

An IFDS-based data-flow analysis propagates data-flow facts along the edges
of a control flow supergraph such as the one in Figure~\ref{fig:examplesupergraph}. The
IFDS algorithm was carefully designed to avoid infeasible paths that may arise in the
presence of multiple calls to the same method. However, in this example all methods are
called in exactly one place, so IFDS is unable to eliminate data flow along any of the
paths shown in the figure. As a result, IFDS-based taint analysis algorithms such as
\cite{DBLP:conf/issta/GuarnieriPTDTB11,DBLP:conf/pldi/ArztRFBBKTOM14} would report 
that the secret value read on line~\ref{line:Afoo}
might flow to the print statement on line~\ref{line:Bbar}.

As we discussed previously, the calls to \code{foo()} and \code{bar()} may dispatch
to different implementations of these methods in classes \code{A} and \code{B}, 
because the variable \code{a} that serves as the receiver for the call may be bound to
 objects of type \code{A} or type \code{B} at run time. 
However, consider the fact that the methods \code{foo()} and \code{bar()} are invoked
on \textit{the same object}. This means that the behaviours of the two method calls
are \textit{correlated}: if the call to \code{foo()} dispatches to \code{A.foo()},
then the call to \code{bar()} must dispatch to \code{A.bar()}, and if the call
to \code{foo()} dispatches to \code{B.foo()}, then the call to \code{bar()} must 
dispatch to \code{B.bar()}.  Consequently, paths such as the one highlighted in
Figure~\ref{fig:examplesupergraph} where the call to \code{foo()} dispatches 
to \code{A.foo()} and where the call to \code{bar()} dispatches to \code{B.bar()}
are infeasible.

The main contribution of this paper is an algorithm for transforming an IFDS problem 
into an IDE problem that expresses the feasibility of paths
in light of correlated calls.
Our approach associates with each edge in an
interprocedural CFG a function that records the types of 
variables that are used as the receiver of correlated method calls. Paths that 
are composed of edges in which the same receiver expression has different types
are infeasible, and the propagation of data-flow facts along such paths is
prevented. Applying our technique to an IFDS-based taint analysis would enable
the resulting IDE-based taint analysis to determine that no secret value can flow from
line~\ref{line:Afoo} to the print statement on line~\ref{line:Bbar}.

In summary, the example discussed in this section shows how the precision of 
IFDS-based taint analysis can be improved by taking into account how paths
become infeasible in the presence of correlated calls. In particular, we have
shown how a false positive reported by a standard IFDS-based algorithm is eliminated.
While the discussion in this section has focused on the specific problem of taint analysis,
we would like to emphasize that our technique generally applies to \textit{any}
data-flow-analysis problem that can be expressed in the IFDS framework. This includes
many common analysis tasks such as reaching definitions, constant propagation, slicing,
typestate analysis, pointer analysis, and lightweight
shape analysis.

@@

However, the implementation of \code{TraversableOnce.toArray} is actually correct because the above
code is guarded with a test: \code{if (this.isTraversableAgain) ...}
%\inputMintedNoLNs{scala}{isTraversable.scala}
When the \code{isTraversableAgain} method returns false, as it does for
an iterator, the \code{toArray} method uses a different
(less efficient) implementation. The bug report would therefore be a false positive. 
The \code{isTraversableAgain} method is easy to analyze: it returns the constant
true in a collection and the constant false in an iterator. However, in order
to eliminate the false positive bug report, an analysis would need to rule out infeasible
paths using correlated calls. Specifically, the following path triggers the bug, but
is infeasible: first, call \code{isTraversableAgain} on a collection, returning
true, then call \code{size} and \code{copyToArray} on an iterator. Our correlated
calls analysis could determine that this path is infeasible because it calls the
collection version of \code{isTraversableAgain} but the iterator versions of
\code{size} and \code{copyToArray}.

The relevant code from \textsf{TraversableOnce} and other related traits is shown
in Figure~\ref{fig:traversableonce} in the Appendix.

>>>>

\section{Motivation}
  \label{sec:MotivatingExample}

We illustrate our approach using a small example that
applies our technique to improve the precision of taint analysis.
A taint analysis computes how string values
may flow from ``sources'', which are typically statements that read untrusted input, 
to ``sinks'', which are typically security-sensitive
operations such as calls to 
a database. In previous research~\cite{DBLP:conf/issta/GuarnieriPTDTB11,DBLP:conf/pldi/ArztRFBBKTOM14}, 
taint analysis algorithms have been formulated as IFDS problems.

@@

Figure~\ref{list:ccexample} shows a small Java program.
%that we will use to illustrate
%how our technique improves the precision of a simple taint analysis.
The program
declares a class \code{A} with a subclass \code{B},  where \code{A} defines methods 
\code{foo()} and \code{bar()} that are overridden in \code{B}.  
%To keep the 
%example small and self-contained, it is 
We assume  that secret values are created by 
an unspecified function \code{secret()}, which is called in \code{A.foo()} on 
line~\ref{line:Afoo}. 
%Furthermore, it is assumed that 
Any write to standard output 
%via calls \code{System.out.println()} such as the one in method \code{B.bar()} 
%on line~\ref{line:Bbar} 
is assumed to be a sink (e.g. the call to \code{System.out.println()} in code{B.bar()}.
%a security-sensitive operation.
Depending on the number of 
arguments passed to the program, the \code{main()} method of the example program creates 
either an \code{A}-object or a \code{B}-object%
%on line~\ref{line:createObject}
. The 
program then calls \code{foo()} on this object
on line~\ref{line:callfoo}, which is 
followed by a call to \code{bar()} on the same object%
%on line~\ref{line:callbar}
.

%The specific question that we would like to answer for the example program of
%Figure~\ref{list:ccexample} is the following:
We wish to answer the following question: Is it possible for the untrusted value 
that is read on line~\ref{line:Afoo} to flow to the print statement% %on line~\ref{line:Bbar}
?
%To determine whether such a flow of tainted data is possible,
Consider the control-flow
supergraph for the example program that is shown in Figure~\ref{fig:examplesupergraph}.
 The nodes in this graph correspond to statements, method entry points (start nodes) and 
method exit points (end nodes). For each method call, the graph contains a 
distinct call-node and a return-node. Edges in the graph reflect intraprocedural control flow, 
flow of control from a caller to a callee (edges from call-nodes to start-nodes), or
flow of control from a callee back to a caller (edges from end-nodes to return-nodes).

In our example, the control flow within each method is straightforward and
all interesting issues arise from interprocedural control flow. In particular,
since the variable \code{a} may point to either an \code{A}-object or a \code{B}-object, 
the call on line~\ref{line:callfoo} may dispatch to either \code{A.foo()} or to \code{B.foo()},
and this is reflected by edges  
  from the node labeled $\highlight{\code{call}_\code{foo}}{greyblue}$ to the nodes labeled
  $\highlight{\code{start}_\code{A.foo()}}{bisque}$ and $\highlight{\code{start}_\code{B.foo()}}{lightsalmonpink}$
and by edges
  from the nodes labeled $\highlight{\code{end}_\code{A.foo}}{bisque}$ and $\highlight{\code{end}_\code{B.foo}}{lightsalmonpink}$ 
  to the node labeled  $\highlight{\code{return}_\code{foo}}{greyblue}$.  
Similarly, there are edges from the node labeled $\highlight{\code{call}_\code{bar}}{greyblue}$ to the nodes 
$\highlight{\code{start}_\code{A.bar()}}{bisque}$ and $\highlight{\code{start}_\code{B.bar()}}{lightsalmonpink}$, and 
edges
  from the nodes labeled $\highlight{\code{end}_\code{A.bar}}{bisque}$ and $\highlight{\code{end}_\code{B.bar}}{lightsalmonpink}$ 
  to the node labeled  $\highlight{\code{return}_\code{bar}}{greyblue}$.

An IFDS analysis propagates data-flow facts along the edges
of a control flow supergraph such as the one in Figure~\ref{fig:examplesupergraph}. The
IFDS algorithm already avoids flow along infeasible paths from one call site, through a target method,
and returning to a different call site of the target method.
However, in this example, all methods are
called in exactly one place, so IFDS is unable to eliminate data flow along any of the
paths shown in the figure. As a result, IFDS-based taint analysis algorithms such as
\cite{DBLP:conf/issta/GuarnieriPTDTB11,DBLP:conf/pldi/ArztRFBBKTOM14} would report 
that the secret value read on line~\ref{line:Afoo}
might flow to the print statement on line~\ref{line:Bbar}.

As we discussed previously, the calls to \code{foo()} and \code{bar()} may dispatch
to the implementations in classes \code{A} and \code{B}, 
because the receiver variable \code{a} may be bound to
 objects of type \code{A} or \code{B} at run time. 
However, the methods \code{foo()} and \code{bar()} are invoked
on \textit{the same object}. Thus the behaviours of the method calls
are \textit{correlated}: if the call to \code{foo()} dispatches to \code{A.foo()},
then the call to \code{bar()} must dispatch to \code{A.bar()}, and analogously
for \code{B.foo()} and \code{B.bar()}.
Consequently, paths such as the one highlighted in
Figure~\ref{fig:examplesupergraph} where the calls dispatch to
\code{A.foo()} and \code{B.bar()}
are infeasible.

Our main contribution is an algorithm for transforming an IFDS problem 
into an IDE problem that expresses the feasibility of paths
in light of correlated calls.
The approach associates with each interprocedural CFG edge 
a function that records the types of 
variables that are used as the receiver of correlated method calls. Paths that 
are composed of edges in which the same receiver expression has different types
are infeasible, and the propagation of data-flow facts along such paths is
prevented. Applying our technique to an IFDS-based taint analysis would enable
the resulting IDE-based taint analysis to determine that no secret value can flow from
line~\ref{line:Afoo} to the print statement on line~\ref{line:Bbar}.

\commentout{
In summary, the example discussed in this section shows how the precision of 
IFDS-based taint analysis can be improved by taking into account how paths
become infeasible in the presence of correlated calls. In particular, we have
shown how a false positive reported by a standard IFDS-based algorithm is eliminated.
}
While the discussion in this section has focused on the specific problem of taint analysis,
our technique generally applies to \textit{any}
data-flow-analysis problem that can be expressed in the IFDS framework. This includes
many common analysis tasks such as reaching definitions, constant propagation, slicing,
typestate analysis, pointer analysis, and lightweight
shape analysis.

@@

However, the implementation of \code{TraversableOnce.toArray} is actually correct because the above
code is guarded with a test: \code{if (this.isTraversableAgain) ...}
%\inputMintedNoLNs{scala}{isTraversable.scala}
When the \code{isTraversableAgain} method returns false, as it does for
an iterator, the \code{toArray} method uses a different
(less efficient) implementation. The bug report would therefore be a false positive. 
The \code{isTraversableAgain} method is easy to analyze: it returns the constant
true in a collection and the constant false in an iterator. However, in order
to eliminate the false positive bug report, an analysis would need to rule out infeasible
paths using correlated calls. Specifically, the following path triggers the bug, but
is infeasible: first, call \code{isTraversableAgain} on a collection, returning
true, then call \code{size} and \code{copyToArray} on an iterator. Our correlated
calls analysis could determine that this path is infeasible because it calls the
collection version of \code{isTraversableAgain} but the iterator versions of
\code{size} and \code{copyToArray}.
The relevant code from \textsf{TraversableOnce} and other related traits is shown
in Figure~\ref{fig:traversableonce} in the Appendix.

### 2015-03-08 sas2015/content/impl.tex

To compare two micro-functions for equality, it suffices to compare the corresponding
sets $I(r)$ and $U(r)$ for all receivers $r$. The following lemma shows that this
implementation of comparison corresponds to equality of the represented micro-functions:
\begin{restatable}{lemma}{equalEq}
\label{lem:equalEq}
    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
    \[
        \forall r\,.\,I(r) = I'(r) \land U(r) = U'(r)
        \iff
        \denote{\setpair{I}{U}} = \denote{\setpair{I'}{U'}}.
    \] 
\end{restatable}
The proofs of all of the lemmas and theorems in the paper are provided in the supplemental
material submitted with the paper.

@@

The meet of two micro-function representations is defined as follows:
$\setpair{I}{U} \sqcap \setpair{I'}{U'} = \setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}$.
The following lemma shows that this implementation corresponds to the meet
of the denoted functions:
\begin{restatable}{lemma}{equalMeet}\label{lem:equalMeet}
\label{lem:equalMeet}
    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
    \[
        \denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}
        = 
        \denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}},
    \]
    where
    $\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}
     =\lambda m.\lambda r.\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)$.
\end{restatable}%\mtodo{I added the definition of the meet of two functions.}

>>>>

To compare two micro-functions for equality, it suffices to compare the corresponding
sets $I(r)$ and $U(r)$ for all receivers $r$. The following lemma shows that this
implementation of comparison corresponds to equality of the represented micro-functions:
\begin{restatable}{lemma}{equalEq}
\label{lem:equalEq}
    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,\\
    $
        \forall r\,.\,I(r) = I'(r) \land U(r) = U'(r)
        \iff
        \denote{\setpair{I}{U}} = \denote{\setpair{I'}{U'}}.
    $
\end{restatable}
The proofs of all of the lemmas and theorems in the paper are provided in the supplemental
material submitted with the paper.

@@

The meet of two micro-function representations is defined as follows:
$\setpair{I}{U} \sqcap \setpair{I'}{U'} = \setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}$.
The following lemma shows that this implementation corresponds to the meet
of the denoted functions:
\begin{restatable}{lemma}{equalMeet}\label{lem:equalMeet}
\label{lem:equalMeet}
    Let $\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}
     =\lambda m.\lambda r.\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)$.
    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,\\
    $
        \denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}
        = 
        \denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}},
    $.
\end{restatable}%\mtodo{I added the definition of the meet of two functions.}

### 2015-03-08 sas2015/figures/fig-cc_edge_fn_example.tex

\begin{figure}[h!]%
  \centering
    \tikzstyle{supergraph}=[
      fill=greyblue,
      rounded corners,
      font=\footnotesize,
      align=right,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{supergraph_y}=[
      fill=bisque,
      rounded corners,
      font=\footnotesize,
      align=left,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{supergraph_f}=[
      fill=lightsalmonpink,
      rounded corners,
      font=\footnotesize,
      align=left,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{description}=[fill=white]
    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
    \tikzstyle{arrowtext}=[font=\tiny,color=black,above]

\hspace*{-10pt}
\begin{tikzpicture}
\scalebox{.8}{
% main method nodes
    \node [supergraph] (st_main) {\textsf{start}$_{\texttt{main}}$};
    \node [supergraph] (asgn_a) [below = \dist of st_main.south east, anchor=east] {\texttt{a = args==null\,?}\\\texttt{new\,A()\,:\,new\,B()}};
    \node [supergraph] (call_foo) [below = \dist of asgn_a.south east, anchor=east] {\textsf{call}$_\texttt{foo}$};
    \node [supergraph] (return_foo) [below = \dist of call_foo.south east,anchor=east] {\textsf{return}$_\texttt{foo}$\\\texttt{v = a.foo()}};
    \node [supergraph] (call_bar) [below = \dist of return_foo.south east, anchor=east] {\textsf{call}$_\texttt{bar}$};
    \node [supergraph] (return_bar) [below = \dist of call_bar.south east, anchor=east] {\textsf{return}$_\texttt{bar}$};
    \node [supergraph] (end_main) [below = \dist of return_bar.south east, anchor=east] {\textsf{end}$_{\texttt{main}}$};

@@

%A.foo method nodes
    \node [supergraph_y] (st_a_foo) [right = 6*\dist of st_main] {\textsf{start}$_{\texttt{A.foo}}$};
    \node [supergraph_y] (return_secret) [below = \dist of st_a_foo.south west, anchor=west] {\texttt{return secret()}};
    \node [supergraph_y] (end_a_foo) [below = \dist of return_secret.south west,anchor = west] {\textsf{end}$_\texttt{A.foo}$};

@@

%A.bar method nodes
    \node [supergraph_y] (st_a_bar) [right = 6*\dist of st_a_foo] {\textsf{start}$_{\texttt{A.bar}}$};
    \node [supergraph_y] (end_a_bar) [below = \dist of st_a_bar.south west,anchor = west] {\textsf{end}$_\texttt{A.bar}$};

@@

%B.foo method nodes
    \node [supergraph_f] (st_b_foo) [right = 6*\dist of call_bar] {\textsf{start}$_{\texttt{B.foo}}$};
    \node [supergraph_f] (return_not_secret) [below = \dist of st_b_foo.south west, anchor=west] {\texttt{return "not secret"}};
    \node [supergraph_f] (end_b_foo) [below = \dist of return_not_secret.south west,anchor = west] {\textsf{end}$_\texttt{B.foo}$};

@@

%B.bar method nodes
    \node [supergraph_f] (st_b_bar) [right = 6*\dist of st_b_foo] {\textsf{start}$_{\texttt{B.bar}}$};
    \node [supergraph_f] (print) [below = \dist of st_b_bar.south west,anchor = west] {\texttt{print(s)}};
    \node [supergraph_f] (end_b_bar) [below = \dist of print.south west,anchor = west] {\textsf{end}$_\texttt{B.bar}$};

    \node [n,label=\texttt{s}] (st_b_bar_s) [left=\nd of st_b_bar.west] {};
    \node [n] (print_s) [left=\nd of print.west] {};
    \node [n] (end_b_bar_s) [left=\nd of end_b_bar.west] {};
    \node [n,label=$\mathbf0$] (st_b_bar_z) [left=\nd of st_b_bar_s] {};
    \node [n] (print_z) [left=\nd of print_s] {};
    \node [n] (end_b_bar_z) [left=\nd of end_b_bar_s] {};
%B.bar method edges
    \path[->](st_b_bar_z) edge (print_z);
    \path[->](print_z) edge (end_b_bar_z);
    \path[->, ultra thick](st_b_bar_s) edge (print_s);
    \path[->](print_s) edge (end_b_bar_s);
    \path[->,dashed](call_bar_z) edge [out=40,in=140,color=lightsalmonpink] (st_b_bar_z);
    \path[->,dashed, ultra thick](call_bar_v) edge [out=20,in=160,color=lightsalmonpink] node[arrowtext,above right=-.4cm and .4cm,rotate=-10]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt B\}]$} (st_b_bar_s);
    \path[->,dashed](end_b_bar_z) edge [out=210,in=-40,color=lightsalmonpink] (return_bar_z);    
}
\end{tikzpicture}
\caption[An example program demonstrating correlated-call edge functions on the $\mathbf0$-node path for Listing~\ref{list:ccexample}]{An example program demonstrating correlated-call edge functions on the $\mathbf0$-node path for Listing~\ref{list:ccexample}. All non-labeled edges are implicitly labeled with identity functions $\id$. The variable $r$ denotes the return value of the \texttt{A.foo} method.}%
  \label{fig:cc_edgefn_example}%  
  \end{figure}

>>>>

%\begin{figure}[h!]%
\vspace{2cm}
  \centering
    \tikzstyle{supergraph}=[
      fill=greyblue,
      rounded corners,
      font=\footnotesize,
      align=right,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{supergraph_y}=[
      fill=bisque,
      rounded corners,
      font=\footnotesize,
      align=left,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{supergraph_f}=[
      fill=lightsalmonpink,
      rounded corners,
      font=\footnotesize,
      align=left,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{description}=[fill=white]
    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
    \tikzstyle{arrowtext}=[font=\tiny,color=black,above]

\hspace*{-10pt}
\begin{tikzpicture}
\scalebox{.8}{
% main method nodes
    \node [supergraph] (st_main) {\textsf{start}$_{\texttt{main}}$};
    \node [supergraph] (asgn_a) [below = \distt of st_main.south east, anchor=east] {\texttt{a = args==null\,?}\\\texttt{new\,A()\,:\,new\,B()}};
    \node [supergraph] (call_foo) [below = \distt of asgn_a.south east, anchor=east] {\textsf{call}$_\texttt{foo}$};
    \node [supergraph] (return_foo) [below = \distt of call_foo.south east,anchor=east] {\textsf{return}$_\texttt{foo}$\\\texttt{v = a.foo()}};
    \node [supergraph] (call_bar) [below = \distt of return_foo.south east, anchor=east] {\textsf{call}$_\texttt{bar}$};
    \node [supergraph] (return_bar) [below = \distt of call_bar.south east, anchor=east] {\textsf{return}$_\texttt{bar}$};
    \node [supergraph] (end_main) [below = \distt of return_bar.south east, anchor=east] {\textsf{end}$_{\texttt{main}}$};

@@

%A.foo method nodes
    \node [supergraph_y] (st_a_foo) [right = 6*\disth of st_main] {\textsf{start}$_{\texttt{A.foo}}$};
    \node [supergraph_y] (return_secret) [below = \distt of st_a_foo.south west, anchor=west] {\texttt{return secret()}};
    \node [supergraph_y] (end_a_foo) [below = \distt of return_secret.south west,anchor = west] {\textsf{end}$_\texttt{A.foo}$};

@@

%A.bar method nodes
    \node [supergraph_y] (st_a_bar) [right = 6*\disth of st_a_foo] {\textsf{start}$_{\texttt{A.bar}}$};
    \node [supergraph_y] (end_a_bar) [below = \distt of st_a_bar.south west,anchor = west] {\textsf{end}$_\texttt{A.bar}$};

@@

%B.foo method nodes
    \node [supergraph_f] (st_b_foo) [right = 6*\disth of call_bar] {\textsf{start}$_{\texttt{B.foo}}$};
    \node [supergraph_f] (return_not_secret) [below = \distt of st_b_foo.south west, anchor=west] {\texttt{return "not secret"}};
    \node [supergraph_f] (end_b_foo) [below = \distt of return_not_secret.south west,anchor = west] {\textsf{end}$_\texttt{B.foo}$};

@@

%B.bar method nodes
    \node [supergraph_f] (st_b_bar) [right = 6*\disth of st_b_foo] {\textsf{start}$_{\texttt{B.bar}}$};
    \node [supergraph_f] (print) [below = \distt of st_b_bar.south west,anchor = west] {\texttt{print(s)}};
    \node [supergraph_f] (end_b_bar) [below = \distt of print.south west,anchor = west] {\textsf{end}$_\texttt{B.bar}$};

    \node [n,label=\texttt{s}] (st_b_bar_s) [left=\nd of st_b_bar.west] {};
    \node [n] (print_s) [left=\nd of print.west] {};
    \node [n] (end_b_bar_s) [left=\nd of end_b_bar.west] {};
    \node [n,label=$\mathbf0$] (st_b_bar_z) [left=\nd of st_b_bar_s] {};
    \node [n] (print_z) [left=\nd of print_s] {};
    \node [n] (end_b_bar_z) [left=\nd of end_b_bar_s] {};
%B.bar method edges
    \path[->](st_b_bar_z) edge (print_z);
    \path[->](print_z) edge (end_b_bar_z);
    \path[->, ultra thick](st_b_bar_s) edge (print_s);
    \path[->](print_s) edge (end_b_bar_s);
    \path[->,dashed](call_bar_z) edge [out=40,in=140,color=lightsalmonpink] (st_b_bar_z);
    \path[->,dashed, ultra thick](call_bar_v) edge [out=20,in=160,color=lightsalmonpink] node[arrowtext,above right=-.4cm and .4cm,rotate=-10]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt B\}]$} (st_b_bar_s);
    \path[->,dashed](end_b_bar_z) edge [out=190,in=-40,color=lightsalmonpink] (return_bar_z);    
}
\end{tikzpicture}
\vspace{-27mm}
\caption[An example program demonstrating correlated-call edge functions on the $\mathbf0$-node path for Listing~\ref{list:ccexample}]{An example program demonstrating correlated-call edge functions on the $\mathbf0$-node path for Listing~\ref{list:ccexample}. All non-labeled edges are implicitly labeled with identity functions $\id$. The variable $r$ denotes the return value of the \texttt{A.foo} method.}%
  \label{fig:cc_edgefn_example}%  
%  \end{figure}
